\startappendix{Appendix}
\label{chapter:appendix}

\section{Event Selections}
\label{sec:evtsel}

Table \ref{tab:sel} summarizes the event selection requirements from the 2015+2016 dataset and the backgrounds they reduce.

\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{c|c|c}
\hline
\hline
Variable & Requirement & Background reduced \\
\hline
Lepton pair  &
Exactly one \epem or \mpmm pair with & -- \\
& leading (subleading) \pt > 30 (20) GeV  & \\
\hline
Third lepton & Veto additional leptons with \pt > 7 GeV  & $WZ$ \\
\hline
$m_{\ell\ell}$ & 76-106 GeV  & $WW$/$Wt$/$t\bar{t}$/$Z\rightarrow \tau \tau$ \\
\hline
\etmiss & > 90 GeV & \Zjets \\
\hline
$\Delta R_{\ell\ell}$ & < 1.8  & \Zjets, $WW$/$Wt$/$t\bar{t}$/$Z\rightarrow \tau \tau$ \\
\hline
$|\Delta\phi(p_\text{T}^{\ell\ell},$\etmiss)| & > 2.7  & \Zjets, $WW$/$Wt$/$t\bar{t}$/$Z\rightarrow \tau \tau$ \\
\hline
Fractional \pt diff. &  < 0.2  & \Zjets \\
\hline
\etmissht & > 0.6 & \Zjets \\
\hline
$b$-jets  & Veto $b$-tagged jets  & $t\bar{t}$ \\
\hline
\hline
\end{tabular}
\end{center}
\caption{Event selections used for the 2015+2016 dataset.}
\label{tab:sel}
\end{table}

\noindent Several variables are calculated from the lepton pair. $m_{\ell\ell}$ and $p_\text{T}^{\ell\ell}$ are the invariant mass and the transverse momentum of the pair, and $\Delta R_{\ell\ell}$ is the angular separation between them, where $\Delta R = \sqrt{(\Delta \eta)^2 + (\Delta \phi)^2}$. The fractional \pt difference = $| p_\text{T}^{\ell\ell} - |\vec{E}_\text{T}^\text{miss} + \sum \vec{p}_\text{T}^\text{jets}| | / p_\text{T}^{\ell\ell}$, and $H_\text{T} = p_\text{T}^\text{jets} + p_\text{T}^{\ell_1} + p_\text{T}^{\ell_2}$.

\clearpage

\section{Calibration Studies on Close-By Jets}
Jet calibration studies were done for my ATLAS authorship qualification task. The purpose of this work was to validate the jet calibration performance for $R = 0.4$ anti-$k_\text{T}$ EM-scale jets in close-by environments. Studies were done on the jet response and resolution for calibrated, close-by jets in \Pythia 8 dijet MC as a function of \DeltaRmin, jet area, and \fCloseby, variables that are used to assess how close-by a jet is. With minimal jet selections and standard $\DeltaR < 0.3$ truth matching, a significant population of low response close-by jets was observed, primarily at low \pt. Several categories of low response close-by jets were investigated. Of the categories investigated, the most important sources of low response were jets with a multi-matched truth jet (one truth jet matched to several jets), and jets with a bad truth matching. Ghost truth association was studied as a robust alternative to \DeltaR truth matching, which can break down in very close-by environments. After removing different sources of low response and switching to ghost truth matching, good agreement was seen in the response for close-by jets with small \DeltaRmin compared to more isolated jets. However some low response jets with small area and/or large \fCloseby remained. Topology and GSC dependence was investigated for these remaining jets, as well as the correlation between \DeltaRmin, area, and \fCloseby.